---
title: "My R Documentation"
author: "Luca Vignali"
date: "Monday, September 29, 2014"
output: html_document
---

# Classes
Class is a basic property of an R Object. The function class()
return the class of the object.

## List of Classes in R

There are five basic "atomic" classes:


* _integer_:    myNumber <- 3L
* _numeric_:    myNumber <- 3
* _complex_:    myComplex <- 1 + 3i
* _character_:  myname <- "Luca Vignali"
* _logical_:    myyes <- TRUE

The instruction class() returns the Object class. For example:

```{r}
myname <- "Luca Vignali"
class(myname)
```

Other very important classes are

* _matrix_:     mymatrix <- matrix(1:9,3,3)
* _data.frame_: myage <- data.frame("Luca Vignali", 43)
* _list_:       mylist <- list(myage, mymatrix)
* _function_:   mysquare <- function(x) {x^2}
* _data.table_: DT[,sum(y),by=x] / DT[,.N,by=COW]

Additional important clasess
* _density_ 
* _xtable_

#### Vectors
Vector is not a class. It is a sequence of objects of the same class.

Vectors can be easily created by combining objects of the same class,
with the instruction c(). 



# Functions
1. table
2. plot
3. pie
4. sample
5. library
6. cbind
7. rbind 
8. density
9. paste
10. print.xtable
11. xtable
12. date
13. head
14. tail
15. xmlSApply
16. xmlRoot
17. xmlName
18. xmlValue
19. xmlSapply
20. xpathSApply (doc,path,FUN,...) 
  1. example xpathSApply(xmldata,"//zipcode",xmlValue)
21. table (df, useNA='ifany'), table(df$pippo,df$pluto) table(df$pippo %in% c(a,b))
22. setkey
23. readLines
24. nchar
25. which
26, sort
27. order
28, arrange (library plyr)
29. str
30. quantile
31. any
32. all
33. colSums, rowSums
34. xtabs
35. ftable
36. object.size
37. seq
38. ifelse
39. cut, breaks
40. cut2 
41. mutate



## Library and Packages management
1. library
2. install.packages

## Functions to process files
1. file.exists("Name of the file or directory")
2. list.files("Name of the directory")
3. dir.create("Name of the directory")
4. download.file(url, destfile, mode)
5. ?connections

## Functions to read/write files csv,xlsx,xml

1. read.table/csv (file, header, sep, row.names, nrows, col.names, skip, colClasses, quote, na.strings)
2. read.xlsx - read.xlsx2 (file, sheetIndex, header, colIndex, rowIndex,)
3. write.xlsx

### Reading and formatting Web Pages and API
_Packages:_ XML, httr

* xmlTreeParse(file,useInternal)
* htmlTreeParse(file, useInternal)
* url (URL, open)
* close
* GET(URL, authenticate("user","PWD"), handle APP)
  * content
  * handle(URL)
* Response [URL]
* oauth_app("twitter", key, secret)
* signoauth1.0(handle, token, token_secret)
* content
* jsonlie::from JSON(toJSON(json1))


6. fromJSON(txt)
7. toJSON(x,pretty=TRUE)
8. fread




You can also embed plots, for example:

```{r, echo=FALSE}
plot(cars)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
